Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-09 ms/response_letter.Rmd

> L99-100 It may bear repeating here why you expect the estimates to match up better for smaller and/or thicker leaves

> L101-102 again, might be worth stating why (even if it is discussed above)

> L107- 113 The description of the sites/data is a little confusing: it seems that there are two datasets: one which includes 3 different sites, and another that includes a fourth site, for which a subset of the samples had additional measurement taken. I recommend clarifying this section to explain the different levels of organization, as well as including some of the methodological data in Table S1 (e.g. number of total samples, whether leaf thickness was measured, leaf punch size).

Thank you.
(different levels of organization?)
We have added columns to explain the number of species, the number of individuals, whether leaf thickness was measured, and leaf punch size in Table S1.

@@

> L148-151 why were the species divided at all? Why not analyze the data as a single group, using leaf area and leaf thickness as (continuous) covariates? Dividing the species into groups this way turns a continuous variable into a categorical one, which is poor statistical practice.

Thank you.
We now only report the linear model that used leaf area and leaf thickness as covariates as noted above.

@@

> Li, Y., Zheng, Y., Ratkowsky, D.A., Wei, H., Shi, P. 2022. Application of an ovate leaf shape model to evaluate leaf bilateral asymmetry and calculate lamina centroid location. Frontiers in Plant Science, 12: 822907. doi: 10.3389/fpls.2021.822907

> Lines 97 and 98: Drop the numerical values of R squared. There is no need to exhibit the results here.

> Lines 105 and 106: Why did you only collect the data in China and Japan. Here, I think, you had better add one to three sentences to explain the feasibility of showing general results for other floras.

Thank you.
We have added MAT and MAP in the main text to support that our dataset covers the wide climate ranges in the distribution of broad-leaved tree species.

@@

> Lines 124 and 125: Why did you maintain leaf petiole in calculating LMA? It is strange for me, because it might inflate LMA given that its definition is dry mass per unit leaf area. What is the meaning for "avoiding thick veins"? Do you mean in the experiment you punch the positions without having the secondary order veins?

The main function of leaves is to deliver a profitable return on the investment that has been made in constructing the leaf (Westoby, Reich and Wright 2013), and thus it is also natural to include leaf petiole in LMA.
According to the trait hand book (Perez-Harguindeguy 2013), either including or excluding petiole will fine.
As long as we checked the TRY data that we have now, the numbers of LMA records for those two measurements are very similar:
the number of records of LMA (or 1/SLA) including petiole is 57,033, and
the number of records of LMA (or 1/SLA) excluding petiole is 59,103.
(add conclusion).

Thank you.
We now more clearly explain that thick veins are secondary order veins.
We have also added detailed LMA measurement protocol in Fig. SX.

@@

> Lines 129-131: Can you class the leaf shapes of 334 woody species you have used? It will affect your sampling positions you are describing here.

We have added detailed LMA measurement protocol in Fig. SX as note above.

> Lines 151-153: I think, a frequency of LA is needed as a supplementary figure to show the feasibility of such division.

### 2022-05-09 ms/LMA_method.Rmd
update ms

*Study sites and plant materials*

We conducted this study in four sites which cover a wide ranges of biomes to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits (see site details in Table S1).
First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
We excluded species that had tiny leaves or leaflets (length <1 cm) because it was not practical to measure leaf disc LMA.
In total, we used `r val$all_sp` woody species and `r val$all_tree` individuals.
The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.

@@

>>>>

*Data sources*

We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Table S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
In total, our data set comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from xxx to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Table S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.

@@

We excluded species that had tiny leaves or leaflets (length <1 cm) because it was not practical to measure leaf disc LMA.

### 2022-05-09 ms/SI.Rmd
update ms

```{r, echo=FALSE}
library(jsonlite)
# for dependency
targets::tar_load(site_info)
#site <- fromJSON("../data/site_info.json")
site <- fromJSON("data/site_info.json")
site |>
  kable(format = "html") |>
  kable_styling()
```

>>>>

```{r, echo=FALSE}
library(jsonlite)
# for dependency
targets::tar_load(site_info)
#site <- fromJSON("../data/site_info.json")
site <- fromJSON("data/site_info.json")
site >
  kable(format = "html") |>
  kable_styling()
```
